Details matter: Similar host galaxies can harbor different merging compact binary populations

### 2016-07-11 paper/paper.tex
Commit changes

\section{Model for compact binary formation}
\label{sec:model}

Binary evolution calculations suggest the detection rate depends sensitively on the assumed metallicity, in conjuction
with other parameters \citep[see,\,e.g.][and references
  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008}.\editremark{New dominik et al}
% POINT: 
%   - final BH spin, mass can change number favored
%   - of course
The detected population of compact binary mergers can further favor low-metallicity environments, e.g. through the total
mass of merging binaries. \jillianremark{The previous sentence is confusing - rephrase?  I have trouble with ``the detected population can further favor low-Z environments'' because that makes no sense.}
% POINT: Simple model to encompass all
To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event detection, motivated by
the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals.  Specifically, we encapsulate all information about
 binary evolution into two  parameterized response functions.  The funciton ${\cal G}(t| Z) =
dN/dt dM_*$ describes how many mergers per unit initial mass occur after a time $t$ since a starburst,
given ambient metallicity $Z$.  The function $p(m_1,m_2|Z)$ is a metallicity-dependent mass distribution for binaries
formed in a metallicity $Z$.
%
Finally, we account for the substantially increased sensitivity of gravitational wave detectors to binaries of larger
chirp mass $\mc=(m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$; see \abbrvPSellipticals.
%
In terms of this response function, we can therefore calculate the relative contribution to the LIGO  event rate $r_D$
due to any individual galaxy via the following formula 
\begin{widetext}
\begin{subequations}
\label{eq:RatePerGalaxy}
\begin{eqnarray}
r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  
 [\int d\mc p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}]
%\\
%% {\cal R}(z)&\equiv &  \int dx {\cal R} p(z)
\end{eqnarray}
\end{subequations}
\end{widetext}
In this expression, the galactic star formation rate
$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$ are galaxy-dependent and drawn from our
simulations.   \editremark{rewrite this to be average chirp mass at a given metallicity}

We parameterize the response function ${\cal G}(t|Z)$ with two factors: (a) an overall efficiency $\lambda$ for forming
binaries;  and (b) a
cumulative delay time distribution $P_t(<t|Z)$, describing the fraction of binaries born at $t=0$ that merge in less
than time $t$ from a population of binaries $Z$:\footnote{For simplicity, we assume the mass and delay time
  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
  excellent approximation for merging BH-BH binaries at solar metallicity.  }
\begin{eqnarray}
G(t,x|Z) &=& \lambda(Z) p_x(x|Z) \frac{dP_t}{dt}(t) 
\end{eqnarray}
Previous studies suggest the number of merging compact binaries $\lambda \delta M_*$ produced by a starburst depends
as a power law on metallicity:
\begin{eqnarray}
\label{eq:LambdaVersusZModel}
\lambda(Z) &=& \lambda_o \text{max}[(Z/Z_\odot)^{-a}, F_{max}] 
\end{eqnarray}
with $a\in [0,3]$ and $F_{max}<10^3$
%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
 (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).
In this paper we only investigate the dependence of rates with metallicity; we therefore  adopt 
\[
\lambda_0 = 10^{-3}/M_\odot
\]
as a typical value for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
%

>>>>

\section{Detection-weighted compact binary formation}
\label{sec:model}

To explore plausible binary detection scenarios, we adopt a parameterized formalism for binary evolution and event
detection in an individual galaxy, motivated by
the detailed studies of  \abbrvPSgrb{} and \abbrvPSellipticals; similar approaches have been used by
\cite{2016arXiv160508783L} and others.

Binary evolution calculations suggest the binary compact object formation rate rate depends sensitively on the assumed metallicity, in conjuction
with other parameters \citep[see,\,e.g.][and references
  therein]{popsyn-LowMetallicityImpact-Chris2008,popsyn-LIGO-SFR-2008,gwastro-EventPopsynPaper-2016}.
% POINT: 
%   - final BH spin, mass can change number favored
%   - of course
Gravitational wave detectors are also far more sensitive to  massive compact binaries, as are  preferentially  formed in low metallicity
environments \citep{PSellipticals,popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}.  As a result, low metallicity
environments can be overwhelmingly efficient factories for detectable black hole binaries
\citep{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014,gwastro-EventPopsynPaper-2016}.  
%
For this reason, our estimates for compact binary coalescence rates must account for how often  different star-forming
conditions occur;  how often compact binaries that can coalesce now can  derive from each environment; and how often LIGO will detect compact
binaries with different masses, all other things being equal.

\begin{widetext}
% POINT:  Model
To characterize how much more likely LIGO will detect coalescing binaries with different masses, we use a common and
naive estimate for the volume to which advanced LIGO is sensitive \citep[see,e.g.,][]{PSellipticals}:\footnote{For
  simplicity, in this calculation we neglect the effects of cosmology; strong field coalescence; and black hole spin;
  see \cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}, \cite{AstroPaper}, or \cite{RatesPaper} for more details.}
\begin{eqnarray}
V(m_1,m_2) = \frac{4\pi}{3} [445 \unit{Mpc}]^3 \int p(m_1,m_2|Z) dm_1 d,m_2 [ (\mc/1.2 M_\odot)^{5/6}]^3
\end{eqnarray}
This expression depends explicitly on an assumed and metallicity-dependent mass distribution for compact object
mergers, through the characteristic chirp mass $\mc_{C}\equiv [\int p(m_1,m_2|Z) dm_1 d,m_2 (\mc/1.2
  M_\odot)^{15/6}]^{5/16}$ .  We calibrate our metallicity-dependent mass distributions to metallicity-dependent binary
evolution calculations presented in \cite{popsyn-LowMetallicityImpact2-StarTrackRevised-2012} and
\cite{popsyn-LowMetallicityImpact2c-StarTrackRevised-2014}; see, e.g., their Table 1 and Figures 5-7.    For neutron stars, we adopt a fiducial neutron star mass of $1.4 M_\odot$ at all metallicities.  For black
hole-neutron star binaries, we 
For the metallicity-dependent where $p(m_1,m_2|Z)$

% POINT:  Model
To characterize how often different star-forming conditions occur, we use our simulations, which provide a galaxy's star formation rate
$\dot{M}_*$ and star formation metallicity distribution $p(\log Z|t)$.

% POINT: 
To characterize how often compact binaries form and coalesc

% POINT: Simple model to encompass all
  Specifically, we encapsulate all information about
 binary evolution into two  parameterized response functions.  The funciton ${\cal G}(t| Z) =
dN/dt dM_*$ describes how many mergers per unit initial mass occur after a time $t$ since a starburst,
given ambient metallicity $Z$.  The function $p(m_1,m_2|Z)$ is a metallicity-dependent mass distribution for binaries
formed in a metallicity $Z$.
%
Finally, we account for the substantially increased sensitivity of gravitational wave detectors to binaries of larger
chirp mass $\mc=(m_1 m_2)^{3/5}/(m_1+m_2)^{1/5}$; see \abbrvPSellipticals.
%
In terms of this response function, we can therefore calculate the relative contribution to the LIGO  event rate $r_D$
due to any individual galaxy via the following formula 
\begin{subequations}
\label{eq:RatePerGalaxy}
\begin{eqnarray}
r_D  &\equiv& \int^{0}_{-T_{univ}} dt' d\log Z  \, [\dot{M}_*(t') p(\log Z|t) ] \times \; {\cal G}(0-t' | Z)  
 [\int d\mc p(\mc|Z) (\mc/1.2 M_\odot)^{15/6}]
%\\
%% {\cal R}(z)&\equiv &  \int dx {\cal R} p(z)
\end{eqnarray}
\end{subequations}
In this expression, the galactic star formation rate
are galaxy-dependent and drawn from our
simulations.   \editremark{rewrite this to be average chirp mass at a given metallicity}

\end{widetext}
We parameterize the response function ${\cal G}(t|Z)$ with two factors: (a) an overall efficiency $\lambda$ for forming
binaries;  and (b) a
cumulative delay time distribution $P_t(<t|Z)$, describing the fraction of binaries born at $t=0$ that merge in less
than time $t$ from a population of binaries $Z$:\footnote{For simplicity, we assume the mass and delay time
  distributions are uncorrelated.  Figure A9 in \abbrvPSgrb{} shows this approximation, while not strictly true, is an
  excellent approximation for merging BH-BH binaries at solar metallicity.  }
\begin{eqnarray}
G(t,x|Z) &=& \lambda(Z) p_x(x|Z) \frac{dP_t}{dt}(t) 
\end{eqnarray}
Previous studies suggest the number of merging compact binaries $\lambda \delta M_*$ produced by a starburst depends
as a power law on metallicity:
\begin{eqnarray}
\label{eq:LambdaVersusZModel}
\lambda(Z) &=& \lambda_o \text{max}[(Z/Z_\odot)^{-a}, F_{max}] 
\end{eqnarray}
with $a\in [0,3]$ and $F_{max}<10^3$
%$\lambda_o F_{max} < 3\times 10^{-4}/M_\odot$
 (see, e.g.\cite{popsyn-LIGO-SFR-2008}, \abbrvKBLowZa).
In this paper we only investigate the dependence of rates with metallicity; we therefore  adopt 
\[
\lambda_0 = 10^{-3}/M_\odot
\]
as a typical value for neutron star compact binaries (see \abbrvPSgrb{}, \abbrvPSellipticals, and \abbrvKBLowZa).
%
